Meta-analysis

### 2019-11-13 03_Preliminary_analysis.Rmd
Updates, remove meta on log values

summary(lm(rainfall_sum ~ grain_yield, 
                             data = rain_dat_sum[rain_dat_sum$location != "Hermitage",]))

@@

@@

>>>>

rain_lm <- lm(rainfall_sum ~ grain_yield, 
                             data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])

summary(rain_lm)

@@

resid_rain_lm <- residuals(rain_lm)

@@

We need to also define the relationship between yield loss and disease severity. When exploring this data we should look primarily at the no spray control plots

```{r yield_x_PMseverity}

PM_MB_means %>%
   filter(fungicide == "control") %>%
   ggplot(aes(x = PM_final_severity, y = grain_yield.t.ha.)) +
   geom_point()+
   geom_smooth(method = "lm")

PM_MB_means %>%
   ggplot(aes(x = PM_final_severity, y = prop_YG)) +
   geom_point()+
   geom_smooth(method = "lm")

### 2019-11-13 04_Prep_data.Rmd
tiny changes to spelling, load libraries, etc
Updates, remove meta on log values

```{r import_data}
source("R/import_data.R")
PM_MB_means <- import_data()
```

@@

write.csv(slim_PM_dat, file = "data/slim_PM_clusterdat.csv", row.names = FALSE)
```

@@

>>>>

```{r import_data}
source("R/import_data.R")
PM_MB_means <- import_data()

@@

slim_PM_dat[slim_PM_dat$spray_management == "Late_plus",]
```

@@

#slimmer_PM_dat <- slim_PM_dat[slim_PM_dat$spray_management != "Late",]

### 2019-11-13 05_MetaAnalysis.Rmd
Updates, remove meta on log values

```{r LME_slimer_cluster_disease_mod}
slimer_PM_dat <- read.csv("data/slimer_PM_clusterdat.csv")

m8 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) +
              (factor(spray_management) | trial_ref), 
           data = slimer_PM_dat)

m9 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + 
              (factor(spray_management) | trial_ref), 
           data = slimer_PM_dat)

m10 <- lmer(log(grain_yield.t.ha*1000) ~ (factor(spray_management) | trial_ref), 
           data = slimer_PM_dat)

@@

```{r}
library(metafor)

slimer_PM_dat <- slimer_PM_dat[!is.na(slimer_PM_dat$yield_error),]
slimer_PM_dat$yi <- log(slimer_PM_dat$grain_yield.t.ha*1000)
slimer_PM_dat$spray_management

PM_mv_AI <- rma.mv(yi,yield_error,
                   mods = spray_management,
                   method = "ML",
                   random = list(~ spray_management | trial_ref),
                   struct = "UN",
                   data = slimer_PM_dat)

PM_mv_AI

@@

>>>>

```{r LME_slimmer_cluster_disease_mod}
library(lme4)
slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")

m8 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) +
              (factor(spray_management) | trial_ref), 
           data = slimmer_PM_dat)

m9 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + 
              (factor(spray_management) | trial_ref), 
           data = slimmer_PM_dat)

m10 <- lmer(log(grain_yield.t.ha*1000) ~ (factor(spray_management) | trial_ref), 
           data = slimmer_PM_dat)

@@

We need to impute the variances

```{r imputing_variances}

table(slimmer_PM_dat$spray_management)

sum(is.na(slimmer_PM_dat$yield_error)) # 14 treatments have no error
sum(!is.na(slimmer_PM_dat$yield_error)) # 152 treatments with error

hist(slimmer_PM_dat$yield_error) # yield error is not normally distributed
hist(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed

# generate yield error values
again <- 0
for(i in seq(from = again, to = 500, by = 0.1)){
if(i == 0){log_Yerror <- vector()}

   x1 <- rnorm(1, mean = mean(log(slimmer_PM_dat$yield_error), na.rm = TRUE), #+ i,
                  sd = sd(log(slimmer_PM_dat$yield_error), na.rm = TRUE)) 
   if(x1 <= -7){again <- i
      next()}
   log_Yerror <- c(log_Yerror,x1)

   if(length(log_Yerror) < 14){again <- i
      next()}

   if(length(log_Yerror) > 14){ stop(message("length of log_Yerror exceeded 14"))}

# Lets plot the values to see if they are significantly different
# First lets convert Variance to standard error for all the variables that have variance recorded
slimmer_PM_dat$yield_SE <- sqrt(slimmer_PM_dat$yield_error)/sqrt(slimmer_PM_dat$n)

# Second; adding the imputed standard errors
slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"] <- sqrt(exp(log_Yerror))/sqrt(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"n"]) # 14 treatments have no error

# all errorbars shoul overlap so they are consistant with the meta-data describing no significant difference bettween treatments
# lets test to make sure
if(max(outer(X = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] - (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
             Y = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] + (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
             FUN = "-")) > 0){
   message(paste("\nWarning!!: Imputed yield errors show significant differences when they should not, rerun chunk", "i =",i))
   log_Yerror <- vector()
   next()
}else{
                message(paste(#"\nA value of",i,"was added to the mean distribution from which imputed erorrs were sampled. This led to 
                   "imputed variances now show no significant distances :)\n Now adding variances to data"))
   slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_error"] <- exp(log_Yerror)
       break()}
}

# # Plot the imputed errors for each trial
# slimmer_PM_dat[is.na(slimmer_PM_dat$),] %>%
#    ggplot(aes(y = grain_yield.t.ha, trial))+
#    #geom_point()+
#    geom_pointrange(ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] - (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
#                   ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] + (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
#                   position = "jitter"
#                  )+
#    ylim(0.2,1.5)
#

```{r meta_1}
library(metafor)

slimmer_PM_dat$yi <- slimmer_PM_dat$grain_yield.t.ha
slimmer_PM_dat$vi <- slimmer_PM_dat$yield_error

slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management)
table(slimmer_PM_dat$spray_management)

PM_mv_AI <- rma.mv(yi,vi,
#                   mods = spray_management,
                   method = "ML",
                   random = ~ spray_management | trial,
                   struct = "UN",
                   data = slimmer_PM_dat)

summary(PM_mv_AI)

@@

```{r meta_2}
# Using trial instead of trial_ref

head(slimmer_PM_dat)

slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha)
slimmer_PM_dat$vi <- log(slimmer_PM_dat$pop_var)
slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management)

table(slimmer_PM_dat$spray_management)

PM_mv_AI <- rma.mv(yi,vi,
#                   mods = spray_management,
                   method = "ML",
                   random = list(~ spray_management | trial),
                   struct = "UN",
                   data = slimmer_PM_dat2)

summary(PM_mv_AI)

```{r inspect_for_outliers}
head(slimmer_PM_dat)

slimmer_PM_dat %>%
#   filter(spray_management == "Late_plus") %>%
   ggplot(aes(prop_yield_gain, fill = spray_management))+
   geom_histogram(alpha = 0.5)

slimmer_PM_dat %>%
   filter(spray_management == "Late_plus") %>%
   ggplot(aes(prop_yield_gain, fill = trial_ref))+
   geom_histogram(alpha = 0.5)

slimmer_PM_dat %>%
   filter(spray_management == "Recommended") %>%
   ggplot(aes(prop_yield_gain, fill = trial_ref))+
   geom_histogram(alpha = 0.5)
